%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience in Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Coordintor} % Job title
    {Riverside County Office of Education} % Organization
    {Riverside, CA} % Location
    {Apr. 2018-Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item RESEARCH AND DATA ANALYSIS
          \begin{itemize}
            \item {Developed regression model and accompanying visualizations of
            district and school-level ELA, Math, and NGSS achievement controlling for
            demographics utilizing R and Shiny interactive visualization toolset with
            a focus on identifying "Positive Outliers" for use by Instructional
            Services Unit}
            \item {Integrated county-wide student CALPADS, CAASPP, ELPAC, and
            Collegeboard data in partnership with UC Riverside for use as part of the
            Haynes Foundation supported research project “Examining Disparities in
            Mathematics Achievement to Promote Equity”}
            \item {}
            \item {Collaborated on design of and implementation of program evaluation of 
            STEMulate Student Program}
          \end{itemize}
          \item LEADERSHIP AND CONTINUOUS IMPROVEMENT
          \begin{itemize}
            \item {Reviewed district Local Control Accountability Plans, with a focus
            on approving LCAP Metrics and language regarding meeting the
            Increased/Improved Services requirement for unduplicated pupils}
            \item {Presented regularly to District LCAP authors on development of
            LCAP metrics, specifically around ongoing monitoring of student outcomes,
            as well as on alignment to statewide accountability systems}
          \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Curriculum and Instruction Coordintor} % Job title
    {Menifee Union School District} % Organization
    {Menifee, CA} % Location
    {Jun. 2016-April 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item RESEARCH AND DATA ANALYSIS
          \begin{itemize}
            \item {Administered virtualized Ubuntu Linux server to provide dashboards
            and dynamic reporting for district stakeholders, utilizing R statistical
            computing software and Shiny dashboard framework,PostgreSQL database and
            Apache Airflow data workflow backend.}
            \item {Implemented Tableau real-time demographic report utilzing PostgreSQL
            query to Illuminate student information system backend.}
            \item {Developed Python-based custom web scraping script to interface
            with EADMS student assessment platform utilizing Selenium to automate
            reporting of completion rates and constructed response grading of
            curriculum linked assessments.}
          \end{itemize}
          \item LEADERSHIP AND CONTINUOUS IMPROVEMENT
          \begin{itemize}
            \item {Authored the District Local Control Accountability Plan with a
            focus on districtwide LCAP metrics, “increased or improved services”
            requirements, and implementation monitoring of actions and services.}
            \item {Provided leadership of the District’s assessment program,
            including the ELPAC, CAASPP, GATE, NAEP, PSAT 8/9, PFT, and local
            benchmark assessments.}
            \item {Coached individual site administrators on interpretation of
            results from CAASPP and CELDT assessments to ensure alignment to district
            LCAP and metrics, and in support of the planning cycle for the Single
            Plan for Student Achievement.}
            \item {Supported the administration of Illuminate SIS through
            collaboration with District staff to ensure data quality for annual CBEDS
            and CALPADS reporting, instructional technology applications through
            Clever, and integration with EADMS assessment platform.}
          \end{itemize}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {TOSA - Compliance Coordinator} % Job title
    {Riverside Unified School District} % Organization
    {Riverside, CA} % Location
    {Aug. 2013-Jun 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item RESEARCH AND DATA ANALYSIS
          \begin{itemize}
            \item {Developed specifications with Technology Team for an English
            learner data report utilizing Microsoft SQL Reporting services,
            distributed monthly to all 2000 teachers in RUSD with both student data,
            as well as a link to appropriate instructional response for students
            based upon that data.}
            \item {Developed custom reports utilizing Geographic Information System
            software QGIS to map Free-Reduced Lunch and English Learner demographic
            data in RUSD.}
            \item {Identified key shortfall in AERIES SIS regarding appropriate
            course placement for over 1000 Academic English Learners. Planned and
            provided professional development regarding best practices for course
            placement for AELs for site administrative teams and counselors.}
          \end{itemize}
          \item LEADERSHIP AND CONTINUOUS IMPROVEMENT
          \begin{itemize}
            \item {Led the district’s online Federal Program Monitoring (FPM) Review
            for the 13-14 school year, and in-person FPM review in the 15-16 school
            year, with primary responsibilities for the Compensatory Education and
            English Learner instruments, mitigating over \$500,000 in potential
            findings through corrective action and successful interaction with FPM
            reviewers.}
            \item {Advised Director and other department staff on budgeting of over
            \$10,000,000 in Title I funds, with primary responsibilities in
            maintaining compliance.}
            \item {Authored LEA Plan Addendum, meeting both state/federal
            requirements while synthesizing three separate academic plans into a
            cohesive narrative of RUSD instructional goals and strategies.}
            \item {Provided technical assistance to sites in completing Single Plans
            for Student Achievement, including model budget practices as well as
            identification of appropriate SMART Goals.}
          \end{itemize}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Director of Bands, Ramona High School} % Job title
    {Riverside Unified School District} % Organization
    {Riverside, CA} % Location
    {Aug. 2009-Jun 2013} % Date(s)
    {}

%---------------------------------------------------------
  \cventry
    {Teacher, West Palms Conservatory} % Job title
    {Victor Elementary School District} % Organization
    {Victorville, CA} % Location
    {Aug. 2008-Jun 2009} % Date(s)
    {}


%---------------------------------------------------------
  \cventry
    {Teacher, Los Banos High School} % Job title
    {Los Banos Unified School District} % Organization
    {Los Banos, CA} % Location
    {Aug. 2006-Jun 2008} % Date(s)
    {}


\end{cventries}

