%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Other Publications} % Role
    {} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems-apa} % Description(s)
        \item {Chitwood, N.R., (2020, January 17). \textit{2019 Riverside County StudentTracker Report}. Riverside County Office of Education.}
        % AP Report \item {Chitwood, N.R., (2020, January 17). \textit{2019 Riverside County StudentTracker Report}. Riverside County Office of Education.}
        \item {Chitwood, N.R., (2019, January 10). \textit{2018 Riverside County StudentTracker Report}. Riverside County Office of Education. https://www.rcoe.us/educational-services/files/2019/01/2018-Riverside-County-StudentTracker-Report.pdf}
        \item {Chitwood, N.R., (2018, April 24). \textit{2017 Riverside County StudentTracker Report}. Riverside County Office of Education. https://www.rcoe.us/educational-services/files/2018/10/RCOE-Student-Tracker-Report.pdf}
      \end{cvitems-apa}
    }

  \cventry
    {Dynamic Visualizations/Dashboards} % Role
    {} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvitems-apa} % Description(s)
        \item {Chitwood, N.R., (2020, February 3). \textit{District Model 2019} [Shiny Dashboard]. Riverside County Office of Education. https://riverside.shinyapps.io/DistrictsModel2019/}
        \item {Chitwood, N.R., (2019, November 22). \textit{Schools Model 2019} [Shiny Dashboard]. Riverside County Office of Education. https://riverside.shinyapps.io/SchoolModel2019/}
        \item {Chitwood, N.R., (2019, November 19). \textit{CSI-ATSI School Report - 2019-2020 Identification Cycle}. [Shiny Dashboard]. Riverside County Office of Education. https://riverside.shinyapps.io/CSI-ATSI-2019/}
        \item {Chitwood, N.R., (2019, November 8). \textit{CA School Dashboard Multiyear Report}. [Shiny Dashboard]. Riverside County Office of Education. https://riverside.shinyapps.io/Dashboard\_MultiYear/}
        \item {Chitwood, N.R., (2019, August 28). \textit{CSI-ATSI School Report - 2018-2019 Identification Cycle} [Shiny Dashboard]. Riverside County Office of Education. https://riverside.shinyapps.io/CSI-ATSI/}
        \item {Chitwood, N.R., (2018, October 4). \textit{Schools Model 2018} [Shiny Dashboard]. Riverside County Office of Education. https://riverside.shinyapps.io/SchoolModel2018/}
        \item {Chitwood, N.R., (2018, April 18). \textit{Great Schools Model} [Shiny Dashboard]. Riverside County Office of Education. https://riverside.shinyapps.io/GreatSchools/}
      \end{cvitems-apa}
    }
    %---------------------------------------------------------
\end{cventries}
