%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\cvsubsection {Technical Reports and Other Manuscripts}
%---------------------------------------------------------
    \begin{pubitems} % Description(s)
      \item {Chitwood, N.R. (2020). \textit{2019 Riverside County StudentTracker Report}. Riverside County Office of Education.}
      \item {Chitwood, N.R. (2019). \textit{2019 GeoLead Differentiated Assistance Student Group Comparison Report}. Riverside County Office of Education.}
      \item {Chitwood, N.R. (2019). \textit{2019 GeoLead Differentiated Assistance Trend Report}. Riverside County Office of Education.}
      \item {Chitwood, N.R. (2019). \textit{2019 Riverside County PSAT/AP Potential report}. Riverside County Office of Education.}
      \item {Chitwood, N.R. (2019). \textit{2018 Riverside Country Chronic Absenteeism Report}. Riverside County Office of Education.}
      \item {Chitwood, N.R. (2019). \textit{2018 Riverside County StudentTracker Report}. Riverside County Office of Education. \url{https://www.rcoe.us/educational-services/files/2019/01/2018-Riverside-County-StudentTracker-Report.pdf}}
      \item {Chitwood, N.R. (2018). \textit{2018 Riverside County PSAT/AP Potential report}. Riverside County Office of Education.}
      \item {Chitwood, N.R. (2018). \textit{2017 Riverside County Advanced Placement Report}. Riverside County Office of Education.}
      \item {Chitwood, N.R. (2018). \textit{2017 Riverside County StudentTracker Report}. Riverside County Office of Education. \url{https://www.rcoe.us/educational-services/files/2018/10/RCOE-Student-Tracker-Report.pdf}}
    \end{pubitems}

\cvsubsection {Dynamic Visualizations/Dashboards}
      \begin{pubitems} % Description(s)
        \item {Chitwood, N.R. (2020, February 3). \textit{District Model 2019: Districts Beating the Odds} [Shiny Dashboard]. Riverside County Office of Education. \url{https://riverside.shinyapps.io/DistrictsModel2019/}}
        \item {Chitwood, N.R. (2019, November 22). \textit{Schools Model 2019: Schools Beating the Odds} [Shiny Dashboard]. Riverside County Office of Education. \url{https://riverside.shinyapps.io/SchoolModel2019/}}
        \item {Chitwood, N.R. (2019, November 19). \textit{CSI-ATSI School Report - 2019-2020 Identification Cycle}. [Shiny Dashboard]. Riverside County Office of Education. \url{https://riverside.shinyapps.io/CSI-ATSI-2019/}}
        \item {Chitwood, N.R. (2019, November 8). \textit{CA School Dashboard Multiyear Report}. [Shiny Dashboard]. Riverside County Office of Education. \url{https://riverside.shinyapps.io/Dashboard\_MultiYear/}}
        \item {Chitwood, N.R. (2019, August 28). \textit{CSI-ATSI School Report - 2018-2019 Identification Cycle} [Shiny Dashboard]. Riverside County Office of Education. \url{https://riverside.shinyapps.io/CSI-ATSI/}}
        \item {Chitwood, N.R. (2019, February 20) \textit{Riverside County Middle School Student Grade Report} [Internal PowerBI Report]. Riverside County Office of Education.}
        \item {Chitwood, N.R. (2018, November 6) \textit{Riverside County Student Mobility Report} [Internal PowerBI Report]. Riverside County Office of Education.}
        \item {Chitwood, N.R. (2018, October 4). \textit{Schools Model 2018} [Shiny Dashboard]. Riverside County Office of Education. \url{https://riverside.shinyapps.io/SchoolModel2018/}}
        \item {Chitwood, N.R. (2018, April 18). \textit{Great Schools Model} [Shiny Dashboard]. Riverside County Office of Education. \url{https://riverside.shinyapps.io/GreatSchools/}}
      \end{pubitems}
    %---------------------------------------------------------
